Notes for Week 9/16/2020 - 9/23/2020

### 2021-02-11 notes/weekly_notes/9.23.20.NotesForWeek.tex
Cleaned up notes folder.

Assume the following.
\begin{enumerate}[label=(K\arabic*)]
	\item
	\label{asmp:kernel}
	$K:[0,\infty) \to [0,\infty)$ is a non-increasing function supported on $[0,1]$, and its restriction to $[0,1]$ is Lipschitz with Lipschitz constant $L_K$. Additionally, it is normalized so that
	\begin{equation*}
	\int_{\Reals^d} K\bigl(\norm{z}\bigr) \,dz = 1,
	\end{equation*}
	and $K(1/2) > 0$. Let $\sigma_{K} := \frac{1}{d}\int_{\Reals^d} \|z\|^2 K(\|z\|) \,dy$.
\end{enumerate}
\begin{enumerate}[label=(OT\arabic*)]
	\item 
	\label{asmp:calder19_1}
	There exists $n^{-1/m} < \wt{\delta} < \frac{1}{4}r$.
	\item 
	\label{asmp:calder19_2} There exists $\theta$ such that $C(\theta + \wt{\delta}) \leq p_{\min}/2$.
	\item
	\label{asmp:r_small_1} For all $x,x' \in \Xset$ such that $\|x - x'\| \leq r$, we have that for $W = B(x,r) \cap B(x',r) \cap \Xset$,
	\begin{equation*}
	\vol(W) \geq a_1(\Xset,d) \cdot \nu_d \biggl(\frac{r}{2}\biggr)^d
	\end{equation*}
	for some constant $A_1(\Xset,d)$. 
	\item
	\label{asmp:r_small_2} For all $x,x' \in \Xset$, we have that $z_{xx'} = \frac{1}{2}x + \frac{1}{2}x' \in \Xset$.
	\item 
	\label{asmp:r_small_3} For any $x \in \Xset$, letting $\mc{B}_x:= (\Xset - x)/r \cap B(0,1)$, we have that $\int_{\mc{B}_x} \psi(\|z\|) \,dz \geq a_1(\Xset,d) \cdot \int_{B(0,1)} \psi(\|z\|) \,dz$.
\end{enumerate}
Very roughly speaking, one can view $\theta + \wt{\delta}$ as an upper bound on the optimal transport distance between $P_n$ and $\wt{P}_n$ and the $\Leb_{\infty}$ distance between $\wt{p}_n$ and $p$.

@@

In Lemma~\ref{lem:first_order_graph_sobolev_seminorm_discretized_lb}, we establish the reverse of Lemma~\ref{lem:first_order_graph_sobolev_seminorm_discretized}. 
\begin{lemma}[c.f. Lemma 14 of \cite{trillos2019}]
	\label{lem:first_order_graph_sobolev_seminorm_discretized_lb}
	Suppose $r$ satisfies~\ref{asmp:r_small_2}. For any $u \in \Leb^2(P_n)$, 
	\begin{equation*}
	\wt{E}_{r - 2\wt{\delta}}\bigl(\wt{\mc{P}}^{\star}u\bigr) \leq \biggl(1 + A_3(d,K,P)\frac{\wt{\delta}}{r}\biggr) b_{r}(u)
	\end{equation*}
\end{lemma}

@@

\begin{theorem}[Proposition~2.11 of \textcolor{red}{(Calder2019)}]
	\label{thm:calder19_2}
	Suppose the assumptions~\ref{asmp:calder19_1} and~\ref{asmp:calder19_2} are satisfied. Then with probability at least $1 - A_1n\exp(-a_1n\theta^2\wt{\delta}^d)$, there exists a probability measure $\wt{P}_n$ with density function $\wt{p}_n: \Xset \to \Reals$ such that
	\begin{equation*}
	\min_{T_{\sharp}\wt{P}_n = P_n} d_{\mc{M}}(x,T(x)) \leq \wt{\delta}
	\end{equation*}
	and
	\begin{equation*}
	\bigl\|\wt{p}_n - p\bigr\|_{\infty} \leq A_1\bigl(\theta + \wt{\delta}\bigr)
	\end{equation*}
\end{theorem}
\textcolor{red}{(TODO)}: Replace this Theorem with it's ``flat'' predecessor.

By Theorem~\ref{thm:calder19_2}, the two energies can be related,
\begin{equation}
\label{eqn:calder19_1}
\bigl(1 - A_1(\theta + \wt{\delta})\bigr) E_r(f) \leq \wt{E}_r(f) \leq \bigl(1 + A_1(\theta + \wt{\delta})\bigr) E_r(f),
\end{equation}
and so can the norms
\begin{equation}
\label{eqn:calder19_2}
\bigl(1 - A_1(\theta + \wt{\delta})\bigr) \|f\|_{\Leb^2(P)}^2 \leq \|f\|_{\Leb^2(\wt{P}_n)}^2 \leq \bigl(1 + A_1(\theta + \wt{\delta})\bigr) \|f\|_{\Leb^2(P)}^2.
\end{equation}

@@

\paragraph{Proof of Lemma~\ref{lem:first_order_graph_sobolev_seminorm_discretized_lb}.}
For brevity, we write $\wt{r} := r - 2\wt{\delta}$. We begin by expanding the energy $\wt{E}_{r - 2\wt{\delta}}\bigl(\wt{\mc{P}}^{\star}u\bigr)$ as a double sum of double integrals,
\wt{E}_{\wt{r}}\bigl(\wt{\mc{P}}^{\star}u\bigr) & = \frac{1}{\wt{r}^{d + 2}} \sum_{i = 1}^{n} \sum_{j = 1}^{n} \int_{U_i} \int_{U_j} \Bigl(u(X_i) - u(X_j)\Bigr)^2 K\biggl(\frac{\|x' - x\|}{\wt{r}}\biggr) \wt{p}_n(x') \wt{p}_n(x) \,dx' \,dx
We next use the Lipschitz property of the kernel $K$---in particular that for $x \in U_i$ and $x' \in U_j$,
K\biggl(\frac{\|x' - x\|}{\wt{r}}\biggr) \leq K\biggl(\frac{\|x_i - x_j\|}{r}\biggr) + \frac{2L_K\wt{\delta}}{\wt{r}} \cdot \1\biggl\{\frac{\|x' - x\|}{\wt{r}}\biggr\}
---to conclude that
\begin{align}
\wt{E}_{\wt{r}}\bigl(\wt{\mc{P}}^{\star}u\bigr) & \leq \frac{1}{n^2\wt{r}^{d + 2}} \sum_{i = 1}^{n} \sum_{j = 1}^{n} \Bigl(u(X_i) - U(X_j)\Bigr)^2 K\biggl(\frac{\|x_i - x_j\|}{r}\biggr) + \frac{2L_K\wt{\delta}}{\wt{r}}\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,\1_{[0,1]}\bigr) \nonumber \\
& \leq \biggl(1 + 4\bigl(2^{d + 2} - 1\bigr)\frac{\wt{\delta}}{r}\biggr) b_r(u) + \frac{2L_K\wt{\delta}}{\wt{r}}\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,\1_{[0,1]}\bigr) \label{pf:lem_first_order_graph_sobolev_seminorm_discretized_1}.
\end{align}
We focus now on the factor of $\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,1_{[0,1]})$. For any $x$ and $x' \in \Xset$ such that $\|x - x'\| \leq r$, note that by assumption $z_{xx'}:= \frac{1}{2}x + \frac{1}{2}x' \in \Xset \cap B(x,\wt{r}/2) \cap B(x',\wt{r}/2)$. Moreover by the triangle inequality
\bigl|f(x) - f(x')\bigr|^2 \leq 2\bigl|f(x) - f(z_{xx'})\bigr|^2 + 2\bigl|f(z_{xx'}) - f(x')\bigr|^2
so that
\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,\1_{[0,1]}\bigr) & \leq \int_{\Xset} \int_{\Xset \cap B(x,r)} \Bigl[ 2\bigl|f(x) - f(z_{xx'})\bigr|^2 +  2\bigl|f(z_{xx'}) - f(x')\bigr|^2\Bigr] \wt{p}_n(x') \wt{p}_n(x) \,dx' \,dx.
Now, by a change of variables along with the Lipschitz property of $p$, we can deduce that
 \int_{\Xset} \int_{\Xset \cap B(x,r)} \bigl|f(x) - f(z_{xx'})\bigr|^2 \wt{p}_n(x') \wt{p}_n(x) \,dx' \,dx & \leq 2^d \bigl(1 + L_p\wt{r}\bigr)\int_{\Xset} \int_{\Xset \cap B(x,r/2)} \bigl|f(x) - f(z)\bigr|^2 \wt{p}_n(z) \wt{p}_n(x) \,dz \,dx \\
 & = 2^d \bigl(1 + L_p\wt{r}\bigr) \wt{E}_{\wt{r}/2}\bigl(f; \1_{[0,1]}\bigr),
and therefore by symmetry
\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,\1_{[0,1]}\bigr) \leq 2^{d + 2} \bigl(1 + L_p\wt{r}\bigr) \wt{E}_{\wt{r}/2}\bigl(f; \1_{[0,1]}\bigr).
Finally, noting that $\wt{E}_{\wt{r}/2}\bigl(f; \1_{[0,1]}) \leq \frac{1}{K(1/2)} \wt{E}_{\wt{r}}\bigl(f)$, the proof is completed by plugging our upper bound on $\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,\1_{[0,1]}\bigr)$ back into~\eqref{pf:lem_first_order_graph_sobolev_seminorm_discretized_1}.
\paragraph{Proof of Lemma~\ref{lem:tau_bound}.}
\mbox{}\\
\mbox{}\\
First prove the estimates of $\tau(x)$, and then upper bound on $\|\nabla\tau(x)\|$. Substituting $z = (x' - x)/r$ and using~\ref{asmp:r_small_3}, we have that
\tau(x) & = \frac{1}{r^d} \int_{\Xset} \psi\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \\
& =  \int_{\mc{B}_x} \psi\bigl(\|z\|\bigr) \,dz \\
& \geq a_1(\Xset,d) \cdot \int_{B(0,1)} \psi(\|z\|) \,dz
We will now show that $\int_{B(0,1)} \psi(\|z\|) \,dz = 1$, which will imply our estimate of $\tau(x)$. To see this identity, note that on the one hand, by converting to polar coordinates and integrating by parts we obtain
\int_{B(0,1)} \psi\bigl(\|z\|\bigr) \,dz = d \nu_d \int_{0}^{1} \psi(t) t^{d - 1} \,dt = \nu_d \int_{0}^{1} \psi'(t) t^{d} \,dt = \frac{\nu_d}{\sigma_K} \int_{0}^{1} t^{d + 1} K(t) \,dt;
on the other hand, again converting to polar coordinate, we have
\sigma_K = \frac{1}{d} \int_{\Reals^d} \|x\|^2 K(\|x\|) \,dx = \nu_d \int_{0}^{1}t^{d + 1} K(t) \,dt.

@@

>>>>

Assume the following.
\begin{enumerate}[label=(K\arabic*)]
	\item
	\label{asmp:kernel}
	$K:[0,\infty) \to [0,\infty)$ is a non-increasing function supported on $[0,1]$, $K(1) > 0$, and its restriction to $[0,1]$ is Lipschitz with Lipschitz constant $L_K$. Additionally, it is normalized so that
	\begin{equation*}
	\int_{\Reals^d} K\bigl(\norm{z}\bigr) \,dz = 1,
	\end{equation*}
	Let $\sigma_{K} := \frac{1}{d}\int_{\Reals^d} \|z\|^2 K(\|z\|) \,dy$.
\end{enumerate}
\begin{enumerate}[label=(OT\arabic*)]
	\item 
	\label{asmp:calder19_1}
	There exists $n^{-1/m} < \wt{\delta} < \frac{1}{4}r$.
	\item 
	\label{asmp:calder19_2} There exists $\theta$ such that $C(\theta + \wt{\delta}) \leq p_{\min}/2$.
	\item
	\label{asmp:r_small_1} For all $x,x' \in \Xset$ such that $\|x - x'\| \leq r$, we have that for $W = B(x,r) \cap B(x',r) \cap \Xset$,
	\begin{equation*}
	\vol(W) \geq a_1(\Xset,d) \cdot \nu_d \biggl(\frac{r}{2}\biggr)^d
	\end{equation*}
	for some constant $a_1(\Xset,d)$. 
	\item 
	\label{asmp:r_small_3} For any $x \in \Xset$, letting $\mc{B}_x:= (\Xset - x)/r~ \cap~B(0,1)$, we have that $\int_{\mc{B}_x} \psi(\|z\|) \,dz \geq a_1(\Xset,d) \cdot \int_{B(0,1)} \psi(\|z\|) \,dz$.
\end{enumerate}
Very roughly speaking, one can view $\theta + \wt{\delta}$ as an upper bound on the optimal transport distance between $P_n$ and $\wt{P}_n$ and the $\Leb_{\infty}$ distance between $\wt{p}_n$ and $p$.

@@

In Lemma~\ref{lem:first_order_graph_sobolev_seminorm_discretized_lb}, we establish the reverse of Lemma~\ref{lem:first_order_graph_sobolev_seminorm_discretized}. 
\begin{lemma}[c.f. Lemma 14 of \cite{trillos2019}]
	\label{lem:first_order_graph_sobolev_seminorm_discretized_lb}
	Suppose $\frac{\wt{\delta}}{r} \leq \min\bigl\{\frac{1}{4(2^{d + 2} - 1)}, \frac{K(1)}{2L_K}\bigr\}$. Then for any $u \in \Leb^2(P_n)$, 
	\begin{equation*}
	\wt{E}_{r - 2\wt{\delta}}\bigl(\wt{\mc{P}}^{\star}u\bigr) \leq \biggl(1 + A_3(d,K,P)\frac{\wt{\delta}}{r}\biggr) b_{r}(u)
	\end{equation*}
\end{lemma}

@@

\begin{theorem}[Proposition~2.11 of \textcolor{red}{(Calder2019)}]
	\label{thm:calder19_2}
	Suppose the assumptions~\ref{asmp:calder19_1} and~\ref{asmp:calder19_2} are satisfied. Then with probability at least $1 - A_1n\exp(-a_1n\theta^2\wt{\delta}^d)$, there exists a probability measure $\wt{P}_n$ with density function $\wt{p}_n: \Xset \to \Reals$ such that
	\begin{equation*}
	\min_{T_{\sharp}\wt{P}_n = P_n} d_{\mc{M}}(x,T(x)) \leq \wt{\delta}
	\end{equation*}
	and
	\begin{equation}
	\label{eqn:calder19_ot}
	\bigl\|\wt{p}_n - p\bigr\|_{\infty} \leq A_1\bigl(\theta + \wt{\delta}\bigr)
	\end{equation}
\end{theorem}

The assumptions~\ref{asmp:calder19_1} and~\ref{asmp:calder19_2}, as well as the $\Leb^{\infty}$ bound~\eqref{eqn:calder19_ot}, depend on constants which are not explicitly given. To make this dependence more transparent on the geometric parameters of the problem, we restate the Theorem in the flat Euclidean setting; for completeness, we provide a proof in~\textcolor{red}{???}.

\begin{proposition}[Restatement of Proposition~2.11 of \textcolor{red}{(Calder2019)}]
	\label{prop:optimal_transport}
	Suppose $p$ satisfies~\ref{asmp:bounded_lipschitz_density}. Then there exists a probability measure $\wt{P}_n$ with density $\wt{p}_n$ such that for any $\wt{\delta} \geq n^{-1/d}$,
	\begin{equation*}
	\inf_{T: T_{\sharp} \wt{P}_n = P_n} \biggl\{\sup_{x \in \Xset}~\bigl|T(x) - x\bigr|\biggr\} \leq A_2(d,\Xset) \wt{\delta}
	\end{equation*}
	and
	\begin{equation*}
	\|\wt{p}_n - p\|_{\infty} \leq A_2(d,\Xset) L_p \wt{\delta} + \theta p_{\max} \leq A_1(\wt{\delta} + \theta)
	\end{equation*}
	with probability at least $1 - A_2(d,\Xset) n \cdot \exp\bigl\{-a_2(d,\Xset) p_{\min} n\theta^2\wt{\delta}^d\bigr\}$. 
\end{proposition}

By assumption $A_1(\wt{\delta} + \theta) \leq \frac{1}{2}$. Therefore Proposition~\ref{prop:optimal_transport} allows to relate the energies $\wt{E}_r(f)$ and $E_r(f)$:
\begin{equation}
\label{eqn:calder19_1}
\bigl(1 - A_1(\theta + \wt{\delta})\bigr) E_r(f) \leq \wt{E}_r(f) \leq \bigl(1 + A_1(\theta + \wt{\delta})\bigr) E_r(f),
\end{equation}
as well as the norms $\|f\|_{\Leb^2(P)}$ and $\|f\|_{\Leb^2(P_n)}$:
\begin{equation}
\label{eqn:calder19_2}
\bigl(1 - A_1(\theta + \wt{\delta})\bigr) \|f\|_{\Leb^2(P)}^2 \leq \|f\|_{\Leb^2(\wt{P}_n)}^2 \leq \bigl(1 + A_1(\theta + \wt{\delta})\bigr) \|f\|_{\Leb^2(P)}^2.
\end{equation}

@@

\paragraph{Proof of Lemma~\ref{lem:first_order_graph_sobolev_seminorm_discretized_lb}.}
\mbox{} \\
\mbox{} \\
For brevity, we write $\wt{r} := r - 2\wt{\delta}$. We begin by expanding the energy $\wt{E}_{r - 2\wt{\delta}}\bigl(\wt{\mc{P}}^{\star}u\bigr)$ as a double sum of double integrals,
\begin{align*}
\wt{E}_{\wt{r}}\bigl(\wt{\mc{P}}^{\star}u\bigr) & = \frac{1}{\wt{r}^{d + 2}} \sum_{i = 1}^{n} \sum_{j = 1}^{n} \int_{U_i} \int_{U_j} \Bigl(u(X_i) - u(X_j)\Bigr)^2 K\biggl(\frac{\|x' - x\|}{\wt{r}}\biggr) \wt{p}_n(x') \wt{p}_n(x) \,dx' \,dx
\end{align*}
We next use the Lipschitz property of the kernel $K$---in particular that for $x \in U_i$ and $x' \in U_j$,
\begin{equation*}
K\biggl(\frac{\|x' - x\|}{\wt{r}}\biggr) \leq K\biggl(\frac{\|x_i - x_j\|}{r}\biggr) + \frac{2L_K\wt{\delta}}{\wt{r}} \cdot \1\biggl\{\frac{\|x' - x\|}{\wt{r}} \leq 1\biggr\}
\end{equation*}
---to conclude that
\begin{align}
\wt{E}_{\wt{r}}\bigl(\wt{\mc{P}}^{\star}u\bigr) & \leq \frac{1}{n^2\wt{r}^{d + 2}} \sum_{i = 1}^{n} \sum_{j = 1}^{n} \Bigl(u(X_i) - u(X_j)\Bigr)^2 K\biggl(\frac{\|x_i - x_j\|}{r}\biggr) + \frac{2L_K\wt{\delta}}{\wt{r}}\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,\1_{[0,1]}\bigr) \nonumber \\
& \leq \biggl(1 + 4\bigl(2^{d + 2} - 1\bigr)\frac{\wt{\delta}}{r}\biggr) b_r(u) + \frac{2L_K\wt{\delta}}{\wt{r}}\wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u,\1_{[0,1]}\bigr) \nonumber \\
& \leq \biggl(1 + 4\bigl(2^{d + 2} - 1\bigr)\frac{\wt{\delta}}{r}\biggr) b_r(u) + \frac{2L_K\wt{\delta}}{K(1)\wt{r}} \wt{E}_{\wt{r}}(\wt{\mc{P}}^{\star}u\bigr) \nonumber 
\end{align}
or in other words
\begin{align*}
\wt{E}_{\wt{r}}\bigl(\wt{\mc{P}}^{\star}u\bigr) & \leq \biggl(1 - \frac{2L_K\wt{\delta}}{K(1)\wt{r}}\biggr)^{-1}\biggl(1 + 4\bigl(2^{d + 2} - 1\bigr)\frac{\wt{\delta}}{r}\biggr) b_r(u) \\
& \leq \biggl(1 + \frac{2L_K}{K(1)} + 8\bigl(2^{d + 2} - 1\bigr)\biggr) \frac{\wt{\delta}}{r}b_r(u)
\end{align*}
where the second inequality follows from the algebraic identities $(1 - t)^{-1} \leq (1 + 2t)$ for any $0 < t < 1/2$ and $(1 + s)(1 + t) < 1 + 2s + t$ for any $0 < t < 1$ and $s > 0$.

\paragraph{Proof of Lemma~\ref{lem:tau_bound}.}
\mbox{}\\
\mbox{}\\
First prove the estimates of $\tau(x)$, and then upper bound on $\|\nabla\tau(x)\|$. Substituting $z = (x' - x)/r$ and using~\ref{asmp:r_small_3}, we have that
\begin{align*}
\tau(x) & = \frac{1}{r^d} \int_{\Xset} \psi\biggl(\frac{\|x' - x\|}{r}\biggr) \,dx' \\
& =  \int_{\mc{B}_x} \psi\bigl(\|z\|\bigr) \,dz \\
& \geq a_1(\Xset,d) \cdot \int_{B(0,1)} \psi(\|z\|) \,dz
\end{align*}
We will now show that $\int_{B(0,1)} \psi(\|z\|) \,dz = 1$, which will imply our estimate of $\tau(x)$. To see this identity, note that on the one hand, by converting to polar coordinates and integrating by parts we obtain
\begin{align*}
\int_{B(0,1)} \psi\bigl(\|z\|\bigr) \,dz = d \nu_d \int_{0}^{1} \psi(t) t^{d - 1} \,dt = \nu_d \int_{0}^{1} \psi'(t) t^{d} \,dt = \frac{\nu_d}{\sigma_K} \int_{0}^{1} t^{d + 1} K(t) \,dt;
\end{align*}
on the other hand, again converting to polar coordinate, we have
\begin{equation*}
\sigma_K = \frac{1}{d} \int_{\Reals^d} \|x\|^2 K(\|x\|) \,dx = \nu_d \int_{0}^{1}t^{d + 1} K(t) \,dt.
\end{equation*}

@@

\paragraph{Proof of Proposition~\ref{prop:optimal_transport}.}
We start by defining the density $\wt{p}_n$, which will be piecewise constant over a particular partition $\mc{Q}$ of $\Xset$; specifically if $x \in Q$ for $Q \in \mc{Q}$, then
\begin{equation}
\label{pf:prop_optimal_transport_0}
\wt{p}_n(x) := \frac{P_n(Q)}{\vol(Q)}
\end{equation}
where $\vol(\cdot)$ denotes the full-dimensional Lebesgue measure.

We now construct the partition $\mc{Q}$, in progressive degrees of generality on the domain $\Xset.$
\begin{itemize}
	\item In the special case of the unit cube $\Xset = (0,1)^d$, the partition will simply be the collection of cubes
	\set{Q_k: k \in [\wt{\delta}^{-1}]^d} 
	where $Q_k = \wt{\delta}\Bigl([k_1 - 1,k_1] \otimes \cdots \otimes [k_d - 1,k_d]\Bigr)$ and we assume without loss of generality that $\wt{\delta}^{-1} \in \mathbb{N}$.
	\item If $\mc{\Xset}$ is an open, connected set with smooth boundary, then by Proposition 3.2 of \textcolor{red}{GarciaTrillos14}, there exist a finite number $N(\Xset) \in \mathbb{N}$ of disjoint polytopes which cover $\Xset$. Moreover, letting $U_j$ denote the intersection of the $j$th of these polytopes with $\wb{\Xset}$, this proposition establishes that for each $j$ there exists a bi-Lipschitz homeomorphism $\Phi_j: U_j \to [0,1]^d$. We take the collection of
	\mc{Q} = \biggl\{\Phi_j^{-1}(Q_k): j = 1,\ldots,N(\Xset)~~\textrm{and}~~k \in [\wt{\delta}^{-1}]^d\biggr\}
	to be our partition. Denote by $L_{\Phi}$ the maximum of the bi-Lipschitz constants of $\Phi_1,\ldots,\Phi_{N(\Xset)}$.
	\item Finally, in the general case where $\Xset$ is an open, connected set with Lipschitz boundary, then there exists a bi-Lipschitz homeomorphism $\Psi$ between $\Xset$ and a smooth, open, connected set with Lipschitz boundary. Letting $\Phi_j$ and $\wt{Q}_{j,k}$ be as before, we take the collection
	\mc{Q} = \biggl\{\wt{Q}_{j,k} = \Bigl(\Psi^{-1} \circ \Phi_j^{-1}\Bigr)(Q_k): j = 1,\ldots,N(\Xset)~~\textrm{and}~~k \in [\wt{\delta}^{-1}]^d\biggr\}
	to be our partition. Denote by $L_{\Psi}$ the bi-Lipschitz constant of $\Psi$.
\end{itemize}
Let us record a few facts which hold for all $\wt{Q}_{j,k} \in \mc{Q}$, which follow from the bi-Lipschitz properties of $\Phi_j$ and $\Psi$: first that
\begin{equation}
\label{pf:prop_optimal_transport_1}
\diam(\wt{Q}_{j,k}) \leq L_{\Psi} \L_{\Phi} \wt{\delta}
\end{equation}
and second that
\begin{equation}
\label{pf:prop_optimal_transport_2}
\vol(\wt{Q}_{j,k}) \geq \biggl(\frac{1}{L_{\Psi} L_{\Phi}}\biggr)^d \wt{\delta}^d.
\end{equation}
We now use these facts to show that $\wt{P}_n$ satisfies the claims of Proposition~\ref{prop:optimal_transport}. One on the one hand, by the construction~\eqref{pf:prop_optimal_transport_0} clearly there exists a transport map $\wt{T}: \Xset \to \mathbf{X}$ for which every $x \in \wt{Q}_{j,k}$ is moved to a design point $X \in {\bf X} \cap \wt{Q}_{j,k}$, and so by~\eqref{pf:prop_optimal_transport_1}
\sup_{x \in \Xset} \abs{\wt{T}(x) - x} \leq  L_{\Psi} \L_{\Phi} \wt{\delta}.
On the other hand, applying the triangle inequality we have that for $x \in \wt{Q}_{j,k}$
|\wt{p}_n(x) - p(x)| \leq \biggl|\frac{P_n(\wt{Q}_{j,k}) - P(\wt{Q}_{j,k})}{\vol(\wt{Q}_{j,k})}\biggr| + \frac{1}{\vol(\wt{Q}_{j,k})} \int_{\wt{Q}_{j,k}} |p(x') - p(x)| \,dx 
and using the Lipschitz property of $p$ we find that 
\begin{equation}
\label{pf:prop_optimal_transport_3}
\|\wt{p}_n - p\|_{\Leb^{\infty}} \leq \max_{j,k} \biggl|\frac{P_n(\wt{Q}_{j,k}) - P(\wt{Q}_{j,k})}{\vol(\wt{Q}_{j,k})}\biggr| + L_p L_{\Phi} L_{\Psi} \wt{\delta}
\end{equation}
From Hoeffding's inequality and a union bound, we obtain that 
\mathbb{P}\biggl( \bigl|P_n(\wt{Q}) - P(\wt{Q})\bigr| & \leq \theta P(\wt{Q}) \quad \forall \wt{Q} \in \mc{Q} \biggr) \geq 1 - 2 \sharp(\mc{Q}) \cdot \exp\biggl\{-\frac{\theta^2 n \min \{P(\wt{Q})\}}{3}\biggr\} \\
& \geq 1 - \frac{2 N(\Xset)}{\wt{\delta}^d} \cdot \exp\biggl\{-\frac{\theta^2 n p_{\min} \wt{\delta}^d }{3\bigl(L_{\Psi} L_{\Phi}\bigr)^d}\biggr\}.
Noting that by assumption $P(\wt{Q}) \leq p_{\max} \vol(\wt{Q})$ and $\wt{\delta}^{-d} \leq n$, the claim follows upon plugging back into~\eqref{pf:prop_optimal_transport_3}, and setting
a_1(d, \Xset) := \frac{1}{3\bigl(L_{\Psi} L_{\Phi}\bigr)^d}~~\textrm{and}~~A_1(d,\Xset) := \max \Bigl\{2N(\Xset),L_p L_{\Psi} L_{\Phi} \Bigr\}
in the statement of the proposition.
